The Bug Catalog of the Maven Ecosystem

### 2014-02-17 docs/msr.tex
added conclusions

The Maven ecosystem has been previously analyzed by
Raemaekers et al.~\cite{RDV13}
to produce the {\it Maven dependency dataset}.
Apart from basic information like individual methods, classes,
packages and lines of code for every {\sc jar}, this dataset
also includes a database with all the
connections between the aforementioned elements.
%Our work goes a step further and includes for every {\sc jar}
%of the repository, all the software bug that it contains.

@@

>>>>

The Maven ecosystem has been previously analyzed by
Raemaekers et al.~\cite{RDV13}
to produce the {\it Maven dependency dataset}.
Apart from basic information like individual methods, classes,
packages and lines of code for every {\sc jar}, this dataset
also includes a database with all the
connections between the aforementioned elements.

@@

In this paper, we have presented a dataset that contains
for every {\sc jar} of the Maven Central Repository,
all the software bug that it contains among with some
other metadata. We have also shown how our data can be
used to extract results concerning software evolution.
Research concerning the examination of specific bugs
can be facilitated by our dataset. For instance,
we have examined the characteristics of security
bugs in a previous paper, based upon this dataset~\cite{MKLGS13}.

% dimitro@ bkarak: add dataset and source code availability.
% All source code and data are available ...
